---
title: "Brexit Social Media Interaction Dashboard"
output-file: index.html
format:
  dashboard:
    orientation: rows
    scrolling: true
    embed-resources: true
    theme: [cosmo, brexit-dashboard.scss]
---

```{r}
#| label: setup
#| include: false

library(tidyverse)
library(plotly)
library(scales)
library(ggrepel)
library(here)

brexit_data <- read_csv(
  here("data", "Brexit 5000 Sample Anonymized.csv"),
  show_col_types = FALSE
)

brexit_data <- brexit_data %>%
  mutate(
    Commenter_BA_Score = as.numeric(Commenter_BA_Score),
    Commenter_Total_Reactions = readr::parse_number(as.character(Commenter_Total_Reactions)),
    Brexit_Attitude = factor(
      Brexit_Attitude,
      levels = c("Brexiteer", "Remainer", "Unknown")
    ),
    Cross_Cutting_without_Counters = recode(
      Cross_Cutting_without_Counters,
      "Like_Minded" = "Like-minded",
      "Cross_Cutting" = "Cross-cutting",
      "Unknown" = "Unknown"
    ),
    Cross_Cutting_w_Counters = recode(
      Cross_Cutting_w_Counters,
      "Like_Minded" = "Like-minded",
      "Cross_Cutting" = "Cross-cutting",
      "Unknown" = "Unknown"
    ),
    Comment_Type = str_replace_all(Comment_Type, "_", " "),
    Chain_Comment = factor(
      Chain_Comment,
      levels = c(0, 1),
      labels = c("Standalone", "Chain")
    )
  )

n_comments <- nrow(brexit_data)
n_commenters <- n_distinct(brexit_data$Commenter_ID)
like_minded_share <- mean(brexit_data$Cross_Cutting_without_Counters == "Like-minded", na.rm = TRUE)
cross_cutting_share <- mean(brexit_data$Cross_Cutting_without_Counters == "Cross-cutting", na.rm = TRUE)

comment_counts <- brexit_data %>%
  count(Commenter_ID, name = "n_comments") %>%
  arrange(desc(n_comments)) %>%
  mutate(rank = row_number())

pct_once <- mean(comment_counts$n_comments == 1)
pct_two_or_less <- mean(comment_counts$n_comments <= 2)
```

\# Sidebar {.sidebar}

\*\*Project Overview\*\*\
\
This dashboard analyzes \*\*5,000 anonymized Brexit-related social media comments\*\* to examine political identity, participation concentration, conversational structure, and engagement.

\*\*Key Variables\*\*\
\
- \*\*Commenter_BA_Score\*\*: tone score associated with the comment \
- \*\*Brexit_Attitude\*\*: Brexiteer, Remainer, or Unknown \
- \*\*Cross_Cutting_without_Counters\*\*: whether exchange is like-minded or cross-cutting \
- \*\*Commenter_Total_Reactions\*\*: total reactions received by a comment \
\
\*\*Core Questions\*\*\
\
1. Do comment tone scores differ across Brexit political identities? \
2. Is participation broadly shared, or dominated by a small number of users? \
3. Are discussions more like-minded than cross-cutting? \
4. Do comments with stronger tone scores attract more reactions?

\# Dashboard Overview\
\
\## Row {height="150px"}\
\
\### {width="25%"}

```{r}
#| content: valuebox
#| title: "Total Comments"
list(icon = "chat-dots-fill", color = "white", value = comma(n_comments))
```

\### {width="25%"}

```{r}
#| content: valuebox
#| title: "Unique Commenters"
list(icon = "people-fill", color = "white", value = comma(n_commenters))
```

\### {width="25%"}

```{r}
#| content: valuebox
#| title: "Like-Minded Share"
list(icon = "diagram-3-fill", color = "white", value = percent(like_minded_share, accuracy = 0.1))
```

\### {width="25%"}

```{r}
#| content: valuebox
#| title: "Commented Once"
list(icon = "bar-chart-fill", color = "white", value = percent(pct_once, accuracy = 0.1))
```

\# Visualization 1: Aggression by Political Identity\
\
\## Row {.tabset height="520px"}\
\
\### Version 1 {layout-ncol="1"}

```{r}
#| echo: false
p1_v1 <- ggplot(
  brexit_data %>% filter(!is.na(Commenter_BA_Score)),
  aes(x = Commenter_BA_Score, fill = Brexit_Attitude)
) +
  geom_density(alpha = 0.45) +
  labs(
    x = "Commenter BA score",
    y = "Density"
  ) +
  theme_minimal(base_size = 13)

ggplotly(p1_v1, tooltip = c("x", "y")) %>%
  config(displayModeBar = FALSE)

```

### Version 2 {layout-ncol="1"}

```{r}
#| echo: false
agg_summary <- brexit_data %>%
  filter(!is.na(Commenter_BA_Score)) %>%
  group_by(Brexit_Attitude) %>%
  summarise(mean_aggression = mean(Commenter_BA_Score, na.rm = TRUE), .groups = "drop")

p1_v2 <- ggplot(
  brexit_data %>% filter(!is.na(Commenter_BA_Score)),
  aes(x = Commenter_BA_Score, fill = Brexit_Attitude)
) +
  geom_density(alpha = 0.5, color = NA) +
  geom_vline(
    data = agg_summary,
    aes(xintercept = mean_aggression),
    linetype = "dashed",
    color = "black"
  ) +
  facet_wrap(~ Brexit_Attitude, ncol = 1) +
  labs(
    x = "Commenter BA score",
    y = "Density"
  ) +
  theme_minimal(base_size = 13) +
  theme(legend.position = "none")

ggplotly(p1_v2, tooltip = c("x", "y")) %>%
  config(displayModeBar = FALSE)
```

\### Best Version {layout-ncol="1"}

```{r}
#| echo: false
p1_best <- p1_v2 +
  labs(
    title = "Comment tone differs sharply across Brexit identities",
    subtitle = "Dashed lines show group means; positive scores cluster among Brexiteers and negative scores among Remainers"
  ) +
  scale_fill_manual(values = c(
    "Brexiteer" = "#274c77",
    "Remainer" = "#c97c5d",
    "Unknown" = "#8d99ae"
  ))

ggplotly(p1_best, tooltip = c("x", "y")) %>%
  config(displayModeBar = FALSE)
```

\# Visualization 2: Comment Participation Concentration\
\
\## Row {.tabset height="520px"}\
\
\### Version 1 {layout-ncol="1"}

```{r}
#| echo: false
top10 <- comment_counts %>%
  slice_head(n = 10) %>%
  mutate(user_label = paste("User", row_number()))

p2_v1 <- ggplot(top10, aes(x = reorder(user_label, n_comments), y = n_comments)) +
  geom_col(fill = "steelblue") +
  coord_flip() +
  labs(
    title = "Top 10 commenters",
    x = NULL,
    y = "Number of comments"
  ) +
  theme_minimal(base_size = 13)

ggplotly(p2_v1, tooltip = c("x", "y")) %>%
  config(displayModeBar = FALSE)
```

\### Version 2 {layout-ncol="1"}

```{r}
#| echo: false
p2_v2 <- ggplot(comment_counts, aes(x = rank, y = n_comments)) +
  geom_col(fill = "#d3dce6", width = 0.9) +
  labs(
    x = "Commenter rank",
    y = "Number of comments"
  ) +
  theme_minimal(base_size = 13)

ggplotly(p2_v2, tooltip = c("x", "y")) %>%
  config(displayModeBar = FALSE)
```

\### Best Version {layout-ncol="1"}

```{r}
#| echo: false
top_users <- comment_counts %>%
  slice_max(n_comments, n = 8) %>%
  mutate(label = paste("P", rank))

p2_best <- ggplot(comment_counts, aes(x = rank, y = n_comments)) +
  geom_col(fill = "#dbe5ef", width = 0.9) +
  geom_col(data = top_users, fill = "#c97c5d", width = 0.9) +
  geom_text_repel(
    data = top_users,
    aes(label = label),
    size = 3.5,
    box.padding = 0.3,
    segment.color = "gray50"
  ) +
  labs(
    title = "Participation is highly unequal",
    subtitle = "Most users commented once, while a small minority contributed repeatedly",
    x = "Commenter rank",
    y = "Number of comments"
  ) +
  theme_minimal(base_size = 13) +
  theme(
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank()
  )

ggplotly(p2_best, tooltip = c("x", "y")) %>%
  config(displayModeBar = FALSE)
```

\# Visualization 3: Like-Minded vs Cross-Cutting Exchange\
\
\## Row {.tabset height="520px"}\
\
\### Version 1 {layout-ncol="1"}

```{r}
#| echo: false
exchange_summary <- brexit_data %>%
  count(Cross_Cutting_without_Counters) %>%
  mutate(prop = n / sum(n))

p3_v1 <- ggplot(exchange_summary, aes(x = Cross_Cutting_without_Counters, y = n, fill = Cross_Cutting_without_Counters)) +
  geom_col() +
  theme_minimal(base_size = 13)

ggplotly(p3_v1, tooltip = c("x", "y")) %>%
  config(displayModeBar = FALSE)
```

\### Version 2 {layout-ncol="1"}

```{r}
#| echo: false
p3_v2 <- ggplot(exchange_summary, aes(x = reorder(Cross_Cutting_without_Counters, -n), y = n)) +
  geom_col(fill = "#6c8ebf") +
  geom_text(aes(label = comma(n)), vjust = -0.3, size = 4) +
  theme_minimal(base_size = 13)

ggplotly(p3_v2, tooltip = c("x", "y")) %>%
  config(displayModeBar = FALSE)
```

\### Best Version {layout-ncol="1"}

```{r}
#| echo: false
p3_best <- ggplot(exchange_summary, aes(x = reorder(Cross_Cutting_without_Counters, -n), y = n, fill = Cross_Cutting_without_Counters)) +
  geom_col(width = 0.7, show.legend = FALSE) +
  geom_text(aes(label = comma(n)), vjust = -0.3, size = 4) +
  geom_text(aes(y = n * 0.5, label = percent(prop, accuracy = 0.1)), color = "white", size = 4, fontface = "bold") +
  scale_fill_manual(values = c(
    "Like-minded" = "#274c77",
    "Cross-cutting" = "#c97c5d",
    "Unknown" = "#8d99ae"
  )) +
  expand_limits(y = max(exchange_summary$n) * 1.1) +
  labs(
    title = "Brexit discussion was more often like-minded than cross-cutting",
    subtitle = "Like-minded exchanges occur within the same political camp; cross-cutting exchanges occur across disagreement",
    x = "Type of exchange",
    y = "Number of comments"
  ) +
  theme_minimal(base_size = 13) +
  theme(
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank()
  )

ggplotly(p3_best, tooltip = c("x", "y")) %>%
  config(displayModeBar = FALSE)
```

\# Visualization 4: Aggression and Engagement\
\
\## Row {.tabset height="520px"}\
\
\### Version 1 {layout-ncol="1"}

```{r}
#| echo: false
engagement_data <- brexit_data %>%
  filter(
    !is.na(Commenter_BA_Score),
    !is.na(Commenter_Total_Reactions),
    Commenter_Total_Reactions > 0
  )

p4_v1 <- ggplot(engagement_data, aes(x = Commenter_BA_Score, y = Commenter_Total_Reactions)) +
  geom_point(alpha = 0.3) +
  theme_minimal(base_size = 13)

ggplotly(p4_v1, tooltip = c("x", "y")) %>%
  config(displayModeBar = FALSE)

```

\### Version 2 {layout-ncol="1"}

```{r}
#| echo: false
p4_v2 <- ggplot(engagement_data, aes(x = Commenter_BA_Score, y = Commenter_Total_Reactions)) +
  geom_point(color = "gray70", alpha = 0.35, size = 2) +
  geom_smooth(method = "lm", se = TRUE, color = "#274c77") +
  scale_y_log10(labels = comma) +
  theme_minimal(base_size = 13)

ggplotly(p4_v2, tooltip = c("x", "y")) %>%
  config(displayModeBar = FALSE)
```

\### Best Version {layout-ncol="1"}

```{r}
#| echo: false
label_data <- engagement_data %>%
  slice_max(Commenter_Total_Reactions, n = 6) %>%
  mutate(label = paste("Comment", row_number()))

p4_best <- ggplot(engagement_data, aes(x = Commenter_BA_Score, y = Commenter_Total_Reactions)) +
  geom_point(color = "gray75", alpha = 0.35, size = 2) +
  geom_point(data = label_data, color = "#c97c5d", size = 3) +
  geom_smooth(method = "lm", se = TRUE, color = "#274c77") +
  geom_text_repel(
    data = label_data,
    aes(label = label),
    size = 3.5,
    box.padding = 0.3
  ) +
  scale_y_log10(labels = comma) +
  labs(
    title = "Higher-engagement comments often had stronger tone scores",
    subtitle = "Highlighted points mark the most reacted-to comments; reactions are shown on a log scale",
    x = "Commenter BA score",
    y = "Total reactions (log scale)"
  ) +
  theme_minimal(base_size = 13) +
  theme(panel.grid.minor = element_blank())

ggplotly(p4_best, tooltip = c("x", "y")) %>%
  config(displayModeBar = FALSE)
```
