---
title: "viz-2 commenters"
---

```{r}
library(tidyverse)
library(scales)
library(ggrepel)
library(here)

brexit_data <- read_csv(
  here("data", "Brexit 5000 Sample Anonymized.csv")
)

brexit_data <- brexit_data %>%
  mutate(
    Brexit_Attitude = factor(
      Brexit_Attitude,
      levels = c("Brexiteer", "Remainer", "Unknown")
    ),
    Cross_Cutting_without_Counters = recode(
      Cross_Cutting_without_Counters,
      "Like_Minded" = "Like-minded",
      "Cross_Cutting" = "Cross-cutting",
      "Unknown" = "Unknown"
    )
  )

comment_counts <- brexit_data %>%
  count(Commenter_ID, name = "n_comments") %>%
  arrange(desc(n_comments)) %>%
  mutate(
    rank = row_number(),
    participant_label = paste("Participant", rank)
  )

n_users <- n_distinct(brexit_data$Commenter_ID)
pct_once <- mean(comment_counts$n_comments == 1)
pct_two_or_less <- mean(comment_counts$n_comments <= 2)

top10 <- comment_counts %>%
  slice_head(n = 10)

top_users <- comment_counts %>%
  slice_max(n_comments, n = 8) %>%
  mutate(label = paste("P", rank))

```

\## Why this matters\
\
This visualization examines whether participation in Brexit comment discussions is broadly shared or dominated by a small number of highly active users. Participant IDs are anonymized and are \*\*not shown\*\* in the final graph.

## Draft Version

```{r}
ggplot(top10, aes(x = reorder(participant_label, n_comments), y = n_comments)) +
  geom_col(fill = "steelblue") +
  coord_flip() +
  labs(
    title = "Draft: Top 10 commenters",
    x = NULL,
    y = "Number of comments"
  ) +
    theme_minimal()
```

## What was missing in the draft

The draft only showed the ten most active users. While readable, it did not show the full participation pattern, so it was harder to support the claim that a small number of participants dominate the discussion.

## Final version

```{r}
ggplot(comment_counts, aes(x = rank, y = n_comments)) +
  geom_col(fill = "grey85", width = 0.9) +
  geom_col(
    data = top_users,
    fill = "#D55E00",
    width = 0.9
  ) +
  geom_text_repel(
    data = top_users,
    aes(label = label),
    size = 3.5,
    box.padding = 0.3,
    segment.color = "gray50"
  ) +
  labs(
    title = "Participation in Brexit discussions is highly unequal",
    subtitle = "Most users commented once, while a small minority contributed repeatedly",
    x = "Commenter rank",
    y = "Number of comments"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold"),
    plot.subtitle = element_text(color = "gray35"),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank())

```

## Interpretation

This shows that participation is highly concentrated: while many users appear in the discussion, a small minority account for repeated activity. I revised the original top-10 version to show the full ranked distribution so the inequality in participation is visible across the entire dataset.
