---
title: "viz-1-aggression"
format: html
---

```{r}
library(tidyverse)
library(janitor)
library(scales)
library(patchwork)
library(here)
```

```{r}
brexit_data <- read_csv(here("data","Brexit 5000 Sample Anonymized.csv"))
```

## Clean the variables

```{r}
brexit_data <- brexit_data %>%
  mutate(
    
    Brexit_Attitude = factor(
      Brexit_Attitude,
      levels = c("Brexiteer", "Remainer", "Unknown")
    ),
    
    Cross_Cutting_without_Counters = recode(
      Cross_Cutting_without_Counters,
      "Like_Minded" = "Like-minded",
      "Cross_Cutting" = "Cross-cutting",
      "Unknown" = "Unknown"
    ),
    
    Cross_Cutting_w_Counters = recode(
      Cross_Cutting_w_Counters,
      "Like_Minded" = "Like-minded",
      "Cross_Cutting" = "Cross-cutting",
      "Unknown" = "Unknown"
    ),
    
    Comment_Type = str_replace_all(Comment_Type, "_", " "),
    
    Chain_Comment = factor(
      Chain_Comment,
      levels = c(0,1),
      labels = c("Standalone","Chain")
    ))

table(brexit_data$Brexit_Attitude)
table(brexit_data$Cross_Cutting_without_Counters)
```

### Behavioral aggression by Brexit Identity

```{r}
ggplot(
  brexit_data %>% filter(!is.na(Commenter_BA_Score)),
  aes(x = Commenter_BA_Score, fill = Brexit_Attitude)
) +
  geom_density(alpha = 0.5) +
  facet_wrap(~Brexit_Attitude, ncol = 1) +
  labs(
    title = "Behavioral aggression differs across Brexit political identities",
    subtitle = "Higher scores indicate more aggressive or hostile comment language",
    x = "Behavioral aggression score",
    y = "Density",
    fill = "Brexit identity"
  ) +
  theme_minimal()
```

```{r}
brexit_data %>%
  group_by(Brexit_Attitude) %>%
  summarise(
    n_comments = n(),
    mean_aggression = mean(Commenter_BA_Score, na.rm = TRUE),
    median_aggression = median(Commenter_BA_Score, na.rm = TRUE)
  )
```

#Final version

```{r}
agg_summary <- brexit_data %>%
  filter(!is.na(Commenter_BA_Score)) %>%
  group_by(Brexit_Attitude) %>%
  summarise(
    mean_aggression = mean(Commenter_BA_Score, na.rm = TRUE)
  )

ggplot(
  brexit_data %>% filter(!is.na(Commenter_BA_Score)),
  aes(x = Commenter_BA_Score, fill = Brexit_Attitude)
) +
  geom_density(alpha = 0.55, color = NA) +
  geom_vline(
    data = agg_summary,
    aes(xintercept = mean_aggression),
    linetype = "dashed",
    color = "black"
  ) +
  facet_wrap(~Brexit_Attitude, ncol = 1) +
  labs(
    title = "Behavioral aggression differs across Brexit political identities",
    subtitle = "Higher scores indicate more aggressive or hostile comment language; dashed lines show group means",
    x = "Behavioral aggression score",
    y = "Density",
    fill = "Brexit identity"
  ) +
  theme_minimal()
```

```{r}
library(ggrepel)

comment_counts <- brexit_data %>%
  count(Commenter_ID, name = "n_comments") %>%
  arrange(desc(n_comments)) %>%
  mutate(rank = row_number())

top_users <- comment_counts %>%
  slice_max(n_comments, n = 8) %>%
  mutate(label = paste("User", rank))

top_users <- comment_counts %>%
  slice_max(n_comments, n = 8) %>%
  mutate(label = paste("User", rank))

ggplot(comment_counts, aes(x = rank, y = n_comments)) +
  
  geom_col(fill = "grey80", width = 0.9) +
  
  geom_col(
    data = top_users,
    fill = "#C55644",
    width = 0.9
  ) +
  
  geom_text_repel(
    data = top_users,
    aes(label = label),
    size = 3.5,
    box.padding = 0.3
  ) +
  
  labs(
    title = "A small number of users dominate the Brexit comment discussion",
    subtitle = "Most participants comment once, while a few contribute repeatedly",
    x = "Commenter rank",
    y = "Number of comments"
  ) +
  
  theme_minimal(base_size = 14) +
  
  theme(
    plot.title = element_text(face = "bold"),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank()
  )
```

### why this version is better

It fixes several visual problems:

1.  Highlights important information Instead of thousands of identical bars, it highlights the top commenters.

2.  Makes the story clearer The title now tells the story: “A small number of users dominate the discussion.”

3.  Labels extreme cases ggrepel prevents overlapping labels.

This visualization shows that participation in the Brexit discussion is highly concentrated. While thousands of users contributed at least one comment, most posted only once. A small minority of highly active participants contributed many more comments than the average user. I revised the draft visualization to highlight these extreme contributors while keeping the full distribution visible.
