---
title: "Aggression by Political Identity"
format: html
execute:
  echo: false
  warning: false
  message: false
---

```{r}
library(tidyverse)
library(janitor)
library(scales)
library(patchwork)
library(here)
```

```{r}
brexit_data <- read_csv(here("data","Brexit 5000 Sample Anonymized.csv"))
```

This visualization examines whether political identity is associated with differences in comment tone. Understanding this helps show whether discussions are polarized or balanced across groups.

## Clean variables

```{r}
brexit_data <- brexit_data %>%
  mutate(
    
    Brexit_Attitude = factor(
      Brexit_Attitude,
      levels = c("Brexiteer", "Remainer", "Unknown")
    ),
    
    Cross_Cutting_without_Counters = recode(
      Cross_Cutting_without_Counters,
      "Like_Minded" = "Like-minded",
      "Cross_Cutting" = "Cross-cutting",
      "Unknown" = "Unknown"
    ),
    
    Cross_Cutting_w_Counters = recode(
      Cross_Cutting_w_Counters,
      "Like_Minded" = "Like-minded",
      "Cross_Cutting" = "Cross-cutting",
      "Unknown" = "Unknown"
    ),
    
    Comment_Type = str_replace_all(Comment_Type, "_", " "),
    
    Chain_Comment = factor(
      Chain_Comment,
      levels = c(0,1),
      labels = c("Standalone","Chain")
    ))

table(brexit_data$Brexit_Attitude)
table(brexit_data$Cross_Cutting_without_Counters)
```

## Draft Version

### Behavioral aggression by Brexit Identity

```{r}
ggplot(
  brexit_data %>% filter(!is.na(Commenter_BA_Score)),
  aes(x = Commenter_BA_Score, fill = Brexit_Attitude)
) +
  geom_density(alpha = 0.5) +
  facet_wrap(~Brexit_Attitude, ncol = 1) +
  labs(
    title = "Behavioral aggression differs across Brexit political identities",
    subtitle = "Higher scores indicate more aggressive or hostile comment language",
    x = "Behavioral aggression score",
    y = "Density",
    fill = "Brexit identity"
  ) +
  theme_minimal()
```

```{r}
library(knitr)
library(kableExtra)

brexit_data %>%
  group_by(Brexit_Attitude) %>%
  summarise(
    Comments = comma(n()),
    Mean_Aggression = round(mean(Commenter_BA_Score, na.rm = TRUE), 2),
    Median_Aggression = round(median(Commenter_BA_Score, na.rm = TRUE), 2),
    .groups = "drop"
  ) %>%
  rename(
    `Political Identity` = Brexit_Attitude,
    `Number of Comments` = Comments,
    `Mean Aggression Score` = Mean_Aggression,
    `Median Aggression Score` = Median_Aggression
  ) %>%
  kable(
    caption = "Aggression scores by political identity",
    align = "c"
  ) %>%
  kable_styling(
    full_width = FALSE,
    bootstrap_options = c("striped","hover","condensed")
  )

```

The table shows strong polarization in comment tone across Brexit political identities. Brexiteer comments (3,613) have an average aggression score of **0.99** (median = **1**), while Remainer comments (781) average **–0.97** (median = **–1**), indicating clear separation between the two groups. The Unknown group (606 comments) centers at **0**, suggesting neutral or unclear positioning. The close alignment between mean and median values suggests these patterns are consistent across comments rather than driven by a few extreme observations, providing evidence of systematic differences in tone by political identity.

The draft visualization made comparison difficult because all distributions overlapped in one panel. The lack of clear group separation made it difficult to compare differences across political identities. It also did not include reference markers such as means to guide interpretation.

# Final version

```{r}
agg_summary <- brexit_data %>%
  filter(!is.na(Commenter_BA_Score)) %>%
  group_by(Brexit_Attitude) %>%
  summarise(
    mean_aggression = mean(Commenter_BA_Score, na.rm = TRUE)
  )

ggplot(
  brexit_data %>% filter(!is.na(Commenter_BA_Score)),
  aes(x = Commenter_BA_Score, fill = Brexit_Attitude)
) +
  geom_density(alpha = 0.55, color = NA) +
  geom_vline(
    data = agg_summary,
    aes(xintercept = mean_aggression),
    linetype = "dashed",
    color = "black"
  ) +
  facet_wrap(~Brexit_Attitude, ncol = 1) +
  labs(
    title = "Behavioral aggression differs across Brexit political identities",
    subtitle = "Higher scores indicate more aggressive or hostile comment language; dashed lines show group means",
    x = "Behavioral aggression score",
    y = "Density",
    fill = "Brexit identity"
  ) +
  theme_minimal()
```

```{r}
library(ggrepel)

comment_counts <- brexit_data %>%
  count(Commenter_ID, name = "n_comments") %>%
  arrange(desc(n_comments)) %>%
  mutate(rank = row_number())

top_users <- comment_counts %>%
  slice_max(n_comments, n = 8) %>%
  mutate(label = paste("User", rank))

top_users <- comment_counts %>%
  slice_max(n_comments, n = 8) %>%
  mutate(label = paste("User", rank))

ggplot(comment_counts, aes(x = rank, y = n_comments)) +
  
  geom_col(fill = "grey80", width = 0.9) +
  
  geom_col(
    data = top_users,
    fill = "#C55644",
    width = 0.9
  ) +
  
  geom_text_repel(
    data = top_users,
    aes(label = label),
    size = 3.5,
    box.padding = 0.3
  ) +
  
  labs(
    title = "A small number of users dominate the Brexit comment discussion",
    subtitle = "Most participants comment once, while a few contribute repeatedly",
    x = "Commenter rank",
    y = "Number of comments"
  ) +
  
  theme_minimal(base_size = 14) +
  
  theme(
    plot.title = element_text(face = "bold"),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank()
  )
```

### Why this version is better?

It fixes several visual problems:

1.  Highlights important information Instead of thousands of identical bars, it highlights the top commenters.

2.  Makes the story clearer The title now tells the story: “A small number of users dominate the discussion.”

3.  Labels extreme cases ggrepel prevents overlapping labels.

This visualization shows that participation in the Brexit discussion is highly concentrated. While thousands of users contributed at least one comment, most posted only once. A small minority of highly active participants contributed many more comments than the average user. I revised the draft visualization to highlight these extreme contributors while keeping the full distribution visible.
