---
title: "Comment Participation Concentration"
format: html
execute:
  echo: false
  warning: false
  message: false
---

This visualization examines whether participation in Brexit comment discussions is broadly shared or dominated by a small number of highly active users. Participant IDs are anonymized and are \*\*not shown\*\* in the final graph.

```{r}
library(tidyverse)
library(scales)
library(ggrepel)
library(plotly)
library(here)

brexit_data <- read_csv(
  here("data", "Brexit 5000 Sample Anonymized.csv")
)

brexit_data <- brexit_data %>%
  mutate(
    Brexit_Attitude = factor(
      Brexit_Attitude,
      levels = c("Brexiteer", "Remainer", "Unknown")
    ),
    Cross_Cutting_without_Counters = recode(
      Cross_Cutting_without_Counters,
      "Like_Minded" = "Like-minded",
      "Cross_Cutting" = "Cross-cutting",
      "Unknown" = "Unknown"
    )
  )

comment_counts <- brexit_data %>%
  count(Commenter_ID, name = "n_comments") %>%
  arrange(desc(n_comments)) %>%
  mutate(
    rank = row_number(),
    participant_label = paste("Participant", rank)
  )

n_users <- n_distinct(brexit_data$Commenter_ID)
pct_once <- mean(comment_counts$n_comments == 1)
pct_two_or_less <- mean(comment_counts$n_comments <= 2)

top10 <- comment_counts %>%
  slice_head(n = 10)

top_users <- comment_counts %>%
  slice_max(n_comments, n = 8) %>%
  mutate(label = paste("P", rank))


```

## Version 1

```{r}
ggplot(top10, aes(x = reorder(participant_label, n_comments), y = n_comments)) +
  geom_col(fill = "steelblue") +
  coord_flip() +
  labs(
    title = "Draft: Top 10 commenters",
    x = NULL,
    y = "Number of comments"
  ) +
    theme_minimal()
```

## What was missing in the draft

The draft only showed the ten most active users. While readable, it did not show the full participation pattern, so it was harder to support the claim that a small number of participants dominate the discussion.

## Version 2

```{r}
ggplot(comment_counts, aes(x = rank, y = n_comments)) +
  geom_col(fill = "grey85", width = 0.9) +
  geom_col(
    data = top_users,
    fill = "#D55E00",
    width = 0.9
  ) +
  geom_text_repel(
    data = top_users,
    aes(label = label),
    size = 3.5,
    box.padding = 0.3,
    segment.color = "gray50"
  ) +
  labs(
    title = "Participation in Brexit discussions is highly unequal",
    subtitle = "Most users commented once, while a small minority contributed repeatedly",
    x = "Commenter rank",
    y = "Number of comments"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold"),
    plot.subtitle = element_text(color = "gray35"),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank())

```

## What was missing in this draft

This shows that participation is highly concentrated: while many users appear in the discussion, a small minority account for repeated activity. I revised the original top-10 version to show the full ranked distribution so the inequality in participation is visible across the entire dataset.

## Best Version

```{r}
comment_counts <- comment_counts %>%
  mutate(
    top_group = case_when(
      rank <= 10 ~ "Top 10",
      rank <= 50 ~ "Top 11–50",
      TRUE       ~ "Rest"
    ),
    top_group = factor(top_group,
                       levels = c("Top 10", "Top 11–50", "Rest"))
  )

group_colors <- c(
  "Top 10"    = "#e63946",
  "Top 11–50" = "#f4a261",
  "Rest"      = "#cad2c5"
)

p2_best <- ggplot(comment_counts,
    aes(x     = rank,
        y     = n_comments,
        color = top_group,
        text  = paste0(
          "Rank: ", rank, "\n",
          "Comments: ", n_comments, "\n",
          "Group: ", top_group
        ))) +
  geom_segment(aes(xend = rank, yend = 0),
               linewidth = 0.3, alpha = 0.4) +
  geom_point(aes(size = top_group), alpha = 0.9) +
  scale_color_manual(values = group_colors,
                     name   = "Commenter group") +
  scale_size_manual(
    values = c("Top 10" = 4, "Top 11–50" = 2.5, "Rest" = 0.8),
    guide  = "none"
  ) +
  scale_x_continuous(
    labels = comma,
    breaks = c(1, 500, 1000, 2000, 3000, 4000)
  ) +
  scale_y_continuous(labels = comma) +
  annotate(
    "text",
    x        = 400,
    y        = max(comment_counts$n_comments) * 0.90,
    label    = "Top 10 users dominate activity",
    color    = "#e63946",
    size     = 4,
    hjust    = 0,
    fontface = "bold"
  ) +
  labs(
    title    = "A Tiny Group Dominates Comment Activity",
    subtitle = paste0(
      round(pct_once * 100, 1),
      "% of users commented only once; the top 10 account for a disproportionate share"
    ),
    x        = "Commenter Rank",
    y        = "Number of Comments",
    caption  = "Data: Bossetta et al. (2023). Brexit Facebook comments dataset."
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title         = element_text(face = "bold", size = 15,
                                      color = "#1d1d1d", margin = margin(b = 5)),
    plot.subtitle      = element_text(color = "gray35", size = 12,
                                      margin = margin(b = 15)),
    plot.caption       = element_text(color = "gray55", size = 9,
                                      margin = margin(t = 10)),
    legend.position    = "bottom",
    legend.title       = element_text(face = "bold", size = 11),
    legend.text        = element_text(size = 10),
    axis.title         = element_text(size = 12),
    axis.text          = element_text(size = 10, color = "gray30"),
    panel.grid.minor   = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_line(color = "gray90"),
    plot.margin        = margin(t = 15, r = 15, b = 10, l = 10)
  )

ggplotly(p2_best, tooltip = "text") %>%
  config(displayModeBar = FALSE) %>%
  layout(
    legend = list(
      orientation = "h",
      x           = 0,
      y           = -0.15,
      font        = list(size = 12)
    ),
    hoverlabel = list(
      bgcolor     = "white",
      font        = list(size = 12, family = "Arial"),
      bordercolor = "gray80"
    ),
    margin = list(t = 60, b = 60, l = 60, r = 30)
  )
```
