---
title: "Like-Minded vs Cross-Cutting Exchange"
format: html
execute:
  echo: false
  warning: false
  message: false
---

This visualization examines whether Brexit discussion mostly happened among people who shared the same political views or whether people often engaged across disagreement.\
\
A \*\*like-minded exchange\*\* happens when people interact with others in the same political camp.\
\
A \*\*cross-cutting exchange\*\* happens when people engage with people holding different political views.

```{r}
library(tidyverse)
library(scales)
library(here)

brexit_data <- read_csv(
  here("data", "Brexit 5000 Sample Anonymized.csv")
)

brexit_data <- brexit_data %>%
  mutate(
    Brexit_Attitude = factor(
      Brexit_Attitude,
      levels = c("Brexiteer", "Remainer", "Unknown")
    ),
    Cross_Cutting_without_Counters = recode(
      Cross_Cutting_without_Counters,
      "Like_Minded" = "Like-minded",
      "Cross_Cutting" = "Cross-cutting",
      "Unknown" = "Unknown"
    ),
    Cross_Cutting_w_Counters = recode(
      Cross_Cutting_w_Counters,
      "Like_Minded" = "Like-minded",
      "Cross_Cutting" = "Cross-cutting",
      "Unknown" = "Unknown"
    )
  )

exchange_summary <- brexit_data %>%
  count(Cross_Cutting_without_Counters) %>%
  mutate(prop = n / sum(n))
    
```

## Draft version

```{r}
ggplot(exchange_summary, aes(x = Cross_Cutting_without_Counters, y = n, fill = Cross_Cutting_without_Counters)) +
  geom_col() +
  labs(
    title = "Draft: Exchange type in Brexit discussions",
    x = "Exchange type",
    y = "Number of comments"
  ) +
  theme_minimal()
```

### What was missing in the draft

The first version showed the counts, but it did not clearly explain what like-minded and cross-cutting exchange meant. It also did not emphasize the larger story that discussion was much more likely to stay within the same political camp.\

## Final version

```{r}
ggplot(exchange_summary, aes(x = reorder(Cross_Cutting_without_Counters, -n), y = n, fill = Cross_Cutting_without_Counters)) +
  geom_col(width = 0.7, show.legend = FALSE) +
  geom_text(aes(label = comma(n)), vjust = -0.3, size = 4) +
  geom_text(aes(y = n * 0.5, label = percent(prop, accuracy = 0.1)), color = "white", size = 4, fontface = "bold") +
  scale_fill_manual(
    values = c(
      "Like-minded" = "#1f4e79",
      "Cross-cutting" = "#d97706",
      "Unknown" = "#9ca3af"
    )
  ) +
  labs(
    title = "Brexit discussion was more often like-minded than cross-cutting",
    subtitle = "Like-minded exchanges occur within the same political camp; cross-cutting exchanges occur across disagreement",
    x = "Type of exchange",
    y = "Number of comments"
  ) +
  expand_limits(y = max(exchange_summary$n) * 1.1) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold"),
    plot.subtitle = element_text(color = "gray35"),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank()
  )
```

### Why this version is better?

This visualization shows that Brexit discussion was much more likely to occur in like-minded settings than across political disagreement. Out of all coded exchanges, the majority were like-minded rather than cross-cutting. I revised the chart by adding clearer labels, a more informative subtitle, and percentages inside the bars so that readers can immediately understand both the concept and the scale of the pattern.
