---
title: "Aggression and Engagement"
format: html
execute: 
  echo: false
  warning: false
  message: false
---

This visualization examines whether comments with stronger tone received more engagement from other users.\
\
'Commenter_Total_Reactions' measures how many reactions a comment received, while 'Commenter_BA_Score' captures the tone score associated with the comment. Because reaction counts are highly skewed, a few comments receive much more engagement than most others. A log scale makes that pattern easier to interpret.

```{r}
library(tidyverse)
library(scales)
library(ggrepel)
library(here)

brexit_data <- read_csv(
  here("data", "Brexit 5000 Sample Anonymized.csv")
) %>%
  mutate(
    Commenter_BA_Score = as.numeric(Commenter_BA_Score),
    Commenter_Total_Reactions = parse_number(as.character(Commenter_Total_Reactions)),
    Brexit_Attitude = factor(
      Brexit_Attitude,
      levels = c("Brexiteer", "Remainer", "Unknown")
    ),
    Cross_Cutting_without_Counters = recode(
      Cross_Cutting_without_Counters,
      "Like_Minded" = "Like-minded",
      "Cross_Cutting" = "Cross-cutting",
      "Unknown" = "Unknown"
    )
  )

engagement_data <- brexit_data %>%
  filter(
    !is.na(Commenter_BA_Score),
    !is.na(Commenter_Total_Reactions),
    Commenter_Total_Reactions > 0
  )

label_data <- engagement_data %>%
  slice_max(Commenter_Total_Reactions, n = 6) %>%
  mutate(label = paste("Comment", row_number()))
```

## Draft version

```{r}
ggplot(engagement_data, aes(x = Commenter_BA_Score, y = Commenter_Total_Reactions)) +
  geom_point(alpha = 0.3) +
  labs(
    title = "Draft: Aggression and reactions",
    x = "Commenter BA score",
    y = "Total reactions"
  ) +
  theme_minimal()
```

### What was missing in the draft 

The draft used the raw reaction scale, which compressed most points near the bottom because a few comments received very high reaction counts. It also did not help the reader identify unusually high-engagement comments.

## Final Version

```{r}
ggplot(engagement_data, aes(x = Commenter_BA_Score, y = Commenter_Total_Reactions)) +
  geom_point(color = "gray75", alpha = 0.35, size = 2) +
  geom_point(
    data = label_data,
    color = "#C55644",
    size = 3
  ) +
  geom_smooth(method = "lm", se = TRUE, color = "gray20") +
  geom_text_repel(
    data = label_data,
    aes(label = label),
    size = 3.5,
    box.padding = 0.3
  ) +
  scale_y_log10(labels = comma) +
  labs(
    title = "Higher-engagement comments often had stronger tone scores",
    subtitle = "Highlighted points mark the most reacted-to comments; reactions are shown on a log scale",
    x = "Commenter BA score",
    y = "Total reactions (log scale)"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold"),
    plot.subtitle = element_text(color = "gray35"),
    panel.grid.minor = element_blank()
  )
```

### Interpretation

The final visualization shows that engagement is highly concentrated, with most comments receiving modest reaction counts while a small number attract substantially higher engagement. The log transformation makes this unequal distribution visible by preventing highly reacted comments from compressing the rest of the data. Although the relationship between tone and engagement is not strongly linear, several of the most engaged comments display stronger tone scores, suggesting that more strongly expressed opinions may draw greater attention. This indicates that discussion visibility may be shaped not just by participation, but also by the intensity of expressed viewpoints.
